Multi-resolution Neural Field Estimation

### 2011-03-03 Multiresolution_framework/ltx/manuscript.tex
edit to results

Field reconstruction \dean{using the results of the EM algorithm} at different levels of approximations is shown in \figurename{\ref{fig:FieldEstimates}}. \dean{Needs more info. Like that the results are great!} The figure confirms that $j=2$ is adequate to capture the dynamics of the underlying field, where the RMSE converges to a steady value of \dean{xx}. \dean{j=3 seems like where it converges?} The actual connectivity kernel and the decomposition is plotted in \figurename{\ref{fig:KernelEstimate}}. The reconstructed kernel is in good accordance with the actual kernel, where the actual kernel lies inside the confidence interval. The small error in the estimate is attributed to the MRA of the system used to form the estimator.
\begin{figure}[!h] 
	\centering
		\includegraphics[scale=1]{./Graph/Field.pdf}
		\caption{Actual (grey line) and estimated (black line) neural fields at a time instant for different spatial resolutions. (a) $j=0$, $n_x=17$, RMSE = 4.44. (b) $j=1$, $n_x=33$, RMSE = 1.87. (c) $j=2$, $n_x=65$, RMSE = 1.2. (d) $j=3$, $n_x=131$, RMSE = 1.04. (e) $j=4$, $n_x=263$, RMSE=1.04.}
	\label{fig:FieldEstimates}
\end{figure} 
\begin{figure}[!h] 
	\centering
		\includegraphics[scale=1]{./Graph/Kernel.pdf}
		\caption{The actual connectivity kernel is shown with the black solid line. The estimated kernel and confidence interval is shown by the red line and red shaded region ($\pm2$ std.). The 7 weighted kernel basis functions are shown by the black dashed lines.}
	\label{fig:KernelEstimate}
\end{figure}
\section{Discussion}
In this paper, we have presented a novel model-based framework for estimating cortical dynamics from electrophysiological measurements. The novel aspects include...

>>>>

Field reconstruction \dean{using the results of the EM algorithm} at different levels of approximations is shown in \figurename{\ref{fig:FieldEstimates}}. \dean{Needs more info. Like that the results are great!} The figure confirms that $j=3$ is adequate to capture the dynamics of the underlying field, where the RMSE converges to a steady value of \dean{1.04}.  The actual connectivity kernel and the decomposition is plotted in \figurename{\ref{fig:KernelEstimate}}. The reconstructed kernel is in good accordance with the actual kernel, where the actual kernel lies inside the confidence interval. The small error in the estimate is attributed to the MRA of the system used to form the estimator.
\begin{figure}[!h] 
	\centering
		\includegraphics[scale=1]{./Graph/Field.pdf}
		\caption{Actual (grey line) and estimated (black line) neural fields at a time instant for different spatial resolutions. (a) $j=0$, $n_x=17$, RMSE = 4.44. (b) $j=1$, $n_x=33$, RMSE = 1.87. (c) $j=2$, $n_x=65$, RMSE = 1.2. (d) $j=3$, $n_x=131$, RMSE = 1.04. (e) $j=4$, $n_x=263$, RMSE=1.04.}
	\label{fig:FieldEstimates}
\end{figure} 
\begin{figure}[!h] 
	\centering
		\includegraphics[scale=1]{./Graph/Kernel.pdf}
		\caption{The actual connectivity kernel is shown with the black solid line. The estimated kernel and confidence interval is shown by the red line and red shaded region ($\pm2$ std.). The 7 weighted kernel basis functions are shown by the black dashed lines.}
	\label{fig:KernelEstimate}
\end{figure}
\section{Discussion}
In this paper, we have presented a novel model-based framework for estimating cortical dynamics from electrophysiological measurements. The novel aspects include...
